---
title: "taxyvr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{taxyvr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(taxyvr)
```

This data was acquired curtesy of [The city of Vancouver's Open Data Portal](https://opendata.vancouver.ca/pages/home/). 


This Package contains (currently) 3 main dataframes all with 29 columns :

  * `tax_2020`: This dataset is currently still being updated by the city as it's still the current year. It currently has `r nrow(tax_2020)` rows for properties in 2020
  * `tax_2019`: This contains data regarding the properties in vancouver for the year 2019. The values in this dataset are static and it has `r nrow(tax_2019)` rows. 
  * `tax_2018`: This contains data regarding the properties in vancouver for the year 2018. The values in this dataset are also static and it has `r nrow(tax_2018)` rows.  


The 29 variables included in the dataset are the following, ([Vancouver Open Data Portal documentation page](http://www.gapminder.org/data/documentation/)):

| Variable            | Meaning                                             | Type   | Sample |
|:--------------------|:----------------------------------------------------|:-------|:-------|
| pid                 |   Property identifier                               | chr    | <nobr>014-193-205</nobr>   |
| legal_type          |  Values are 'STRATA', indicating property is part of a Strata Plan,   'LAND' indicating property has a non-strata plan number,   or 'OTHER' for properties with no plan number | chr | STRATA
| folio               |  A 12-digit identifier for purposes of assessment   | dbl    | <nobr>151843410011</nobr>   |
| land_coordinate     |  First 8 digits of BC Assessment's folio number     | dbl    | <nobr>15184341</nobr>   |
| zone_name           |  Name of zoning district                            | chr    | <nobr>M-2</nobr>   |
| zone_category       |  Name of zoning category                            | chr    | <nobr>Industrial</nobr>   |
| block               | Component of legal description                      | chr    | <nobr>155</nobr>   |
| plan                | Component of legal description                      | chr    | <nobr>VAS2438</nobr>   |
| district_lot        | Component of legal description                      | chr    | <nobr>319</nobr>   |
| lot                 | Component of legal description                      | chr    | <nobr>11</nobr>   |
| from_civic_number   | This is the house number, it may be the first number in a range  | chr    | <nobr>3594</nobr>   |
| to_civic_number     | Blank unless it is the last house number in a range | chr    | <nobr>9141</nobr>   |
| street_name         |The name of the street where the property is located | chr    | <nobr>SHAUGHNESSY ST</nobr>   |
| property_postal_code|A series of letters and/or digits that is attached to a property address | chr    | <nobr>V6P 6R9</nobr>   |
| narrative_legal_line3|Describes a property for registration purposes | chr    | <nobr>SHARE IN COM PROP THEREIN</nobr>   |
| narrative_legal_line2|Describes a property for registration purposes | chr    | <nobr>319  NEW WESTMINSTER UNDIV 74/1341</nobr>   |
| narrative_legal_line1|Describes a property for registration purposes | chr    | <nobr>DIV 376/127 LOT 220 PLAN LMS1863 </nobr>   |
| narrative_legal_line4|Describes a property for registration purposes | chr    | <nobr>WESTMINSTER LAND DIST</nobr>   |
| narrative_legal_line5|Describes a property for registration purposes | chr    | <nobr>BLOCK 17, PLAN VAP5928 /nobr>   |
| current_land_value  | The market value of the fee simple interest in land and improvements   | dbl    | <nobr>397000</nobr>   |
| current_improvement_value  | The market value of the fee simple interest in land and improvements   | dbl    | <nobr>107000</nobr>   |
| tax_assessment_year  |Year in effect for Current_Land_Value, Current_Improvement_Value and Tax_Levy | dbl    | <nobr>2018</nobr>   |
| previous_improvement_value  |Year in effect for Current_Land_Value, Current_Improvement_Value and Tax_Levy| dbl    | <nobr>112000</nobr>   |
| previous_land_value  | This value is for the previous assessment year | dbl    | <nobr>262000</nobr>   |
| year_built  |Year that the property was built | dbl    | <nobr>1989</nobr>   |
| big_improvement_year  |Year of major improvement to the property | dbl    | <nobr>1989</nobr>   |
| tax_levy  |This is the total taxes printed on the most recent tax notice.  It includes the City's general levy, levies for all taxing authorities, utilities, local improvements and miscellaneous charges.| dbl    | <nobr>5361.97</nobr>   |
| tax_levy  |This is the total taxes printed on the most recent tax notice.  It includes the City's general levy, levies for all taxing authorities, utilities, local improvements and miscellaneous charges.| dbl    | <nobr>5361.97</nobr>   |
| neighbourhood_code  |This is a 3-digit number assigned by BCA which identifies the neighbourhood for the folio| chr    | <nobr>018</nobr>   |
| report_year  | The report year | dbl    | <nobr>2018</nobr>   |




## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dplyr)
library(taxyvr)


tax_2018 %>% filter(legal_type == "LAND") %>% 
  arrange(desc(current_land_value))
```

or find out the summary statistics of the data:

```{r tax_2018}
summary(tax_2018)
```

## License

taxyvr's data is released under the Open Government Licence - Vancouver license. See their [terms of use](https://opendata.vancouver.ca/pages/licence/). 